Optimal Sizing of Stand-alone Solar PV Systems Through Automated Formal Synthesis Method

### 2019-09-12 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
IEEE Trans on Sustainable Energy paper

\section{Background}
\label{sec:Background}
%-----------------------------------------------------------
Here we explain how to size a stand-alone solar PV system with their respective mathematical model, and what type of criteria or technique is possible to apply for the optimal sizing of PV systems. Furthermore, we present the theory about program synthesis,

@@

A PV system is illustrated in Fig.\ref{fig:blockdiagram}. It identifies the PV generator, batteries, charge controller, inverter, and AC load. The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity. 
For night hours or rainy days, we hold batteries where power can be stored and used. The use of batteries as a storage form implies the presence of a charge controller~\cite{Hansen}. The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required. That converter is called inverter; and the AC load dictates the behavior of AC electrical load from the house that will be fed by the system.

@@

The sizing check stage will ensure that the system meets the standard project steps related 
to critical period solar energy method~\cite{Pinho} and adopting MPPT (Maximum Power Point Tracking) charge controller, which is the most common one in practice, among other sizing techniques and possibilities.

Firstly, we need to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by Eq.~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered~\cite{Pinho} as follows

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{PV systems Optimization Criteria}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%----------------------------------------------------------------------------------------------
\subsection{Stand-alone PV System Optimization Technique}
%----------------------------------------------------------------------------------------------

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Automated Verification Using Model Checking}
\label{sec:AutomatedVerification}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%------------------------------------------------------
\section{Synthesizing optimal sizing of stand-alone solar PV systems}
\label{sec:Method}
%------------------------------------------------------

Algorithm~\ref{alg:verification-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using symbolic model checking. It was adopted the analytical method of optimization, with LCC economical analysis and power reliability based on the critical period criteria.
%
 \begin{algorithm}
 \caption{Synthesis algorithm}
 \begin{algorithmic}[1]
 \renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
  \STATE Initialize variables \\
  \STATE Declare list of PV panels, controllers, batteries, and inverters data and cost \\
%  \STATE Declare list of controllers data and cost \\
%  \STATE Declare list of batteries data and cost \\
%  \STATE Declare list of inverters data and cost \\
  \STATE Declare the maximum possible cost $MaxCost$  \\
  \STATE Declare power demand, power peak, energy consumption \\
  \STATE Declare battery autonomy, deep of discharge, AC voltage \\
  \FOR {$HintCost=0$ to $MaxCost$}
 	\STATE Declare non-deterministic variable to select PV Panel from list \\
 	\STATE Declare non-deterministic variable to select Controller from list \\
 	\STATE Declare non-deterministic variable to select Battery from list \\
 	\STATE Declare non-deterministic variable to select Inverter from list \\ 	
 	\STATE Calculate $E_{corrected}, \, E_{p} $ \\
	\STATE Calculate $N_{TPmin}, \, N_{PSmin}, N_{PPmin} $ \\
 	\STATE Calculate $C_{bank}$ \\
	\STATE Calculate $N_{BS}min, \, N_{BP}min, \, N_{B}total$ \\
	\STATE Requirement enforced by \textbf{assume}$(V_{c})$ \\
 	\STATE Calculate $I_{sc,amb}$ \\
 	\STATE Calculate $I_{c,min}$ \\
 	\STATE Requirement enforced by \textbf{assume}$(I_{c} \wedge V_{in}DC \wedge V_{out}AC)$ \\
%	\STATE Requirement enforced by \textbf{assume}$(V_{in}DC \wedge V_{out}AC )$ \\
%	\STATE Requirement enforced by \textbf{assume}$(V_{out}AC)$ \\
	\STATE Requirement enforced by \textbf{assume}$(Demand \wedge P_{surge})$ \\
%	\STATE Requirement enforced by \textbf{assume}$(P_{surge})$ \\
	\STATE non-deterministic variables hold feasible equipment and cost  \\
	\STATE $F_{obj} \leftarrow  N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost} \, + \, Installation_{Cost} \, + \, batrep_{Cost} \, + \, PWO\&M_{Cost}$ \\
	\STATE Violation check with \textbf{assert}$(F_{obj} > HintCost)$ \\
  \ENDFOR
 \RETURN $(\,)$ 
 \end{algorithmic} 
 \label{alg:verification-algorithm}
 \end{algorithm}
%

@@

%---------------------------------------------------------------------------
\section{Experimental evaluation}
\label{sec:Results}
%---------------------------------------------------------------------------

This section presents the case studies used to evaluate our proposed approach. 
We also compare our approach with a simulation tool, named HOME Pro. 
The version and command-line of each verifier adopted, 
the computing setup, the objectives of the experimental phase, 
and the results itself are also described.

@@

We have performed seven stand-alone PV system case studies to evaluate 
our proposed synthesis approach, as described in the first column of 
Table~\ref{tab1} (named Specification). These case studies were defined 
based on usual electrical load found in riverside communities of the 
Amazon State in Brazil~\cite{abs-1811-09438, Agrener2013}.

@@

%---------------------------------------------------------------------------
\subsection{Comparative Tools} 
%---------------------------------------------------------------------------

The start-of-art verification tool, CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used as our verification engine to compare our approach effectiveness and efficiency. The Simulation tool HOMER Pro version $3.13.1$ was used for comparative purpose.

@@

@@

\item[EQ2] \textbf{(performance)} how do the software verifiers compare to each other?

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparison between Formal Synthesis and HOME Pro}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
\label{sec:Conclusion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\section{Sizing and Optimization of PV Systems}
\label{sec:Background}
%-----------------------------------------------------------

Here we explain the adopted method to size stand-alone solar PV systems, and what type of criteria and technique is possible to apply for the optimal sizing.

@@

A PV system block diagram is illustrated in Fig.\ref{fig:blockdiagram}. %It identifies the PV generator, batteries, charge controller, inverter, and AC load. 
The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity. 
For night hours or rainy days, we hold batteries where power can be stored and used. The use of batteries as a storage form implies the presence of a charge controller~\cite{Hansen}. The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion (inverter) is required. The AC load dictates the behavior of AC electrical load from the house. % that will be fed by the PV system.

@@

%The sizing check stage will ensure that the system meets the standard project steps related  to critical period solar energy method~\cite{Pinho} and adopting MPPT (Maximum Power Point Tracking) charge controller, which is the most common one in practice, among other sizing techniques and possibilities. 
Among the techniques that can be used for the sizing of PV systems, it was adopted here the critical period solar energy method~\cite{Pinho}, with the use of MPPT (Maximum Power Point Tracking) charge controller (which is the most common nowadays). Firstly, we need to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by Eq.~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered~\cite{Pinho} as follows

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{PV Systems Optimization Criteria}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%----------------------------------------------------------------------------------------------
\subsection{PV Systems Optimization Techniques}
%----------------------------------------------------------------------------------------------

@@

%------------------------------------------------------
\section{Automated Formal Synthesis Method}
\label{sec:Method}
%------------------------------------------------------

In this section we present the theory and the methodology created to obtain the optimal sizing of stand-alone solar PV systems through program synthesis.

\subsection{Automated Verification Using Model Checking}
\label{sec:AutomatedVerification}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Algorithm~\ref{alg:verification-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using symbolic model checking. It was adopted the analytical method of optimization, with LCC economical analysis and power reliability based on the critical period criteria.

 \begin{algorithm}
 \caption{Synthesis algorithm}
 \begin{algorithmic}[1]
 \renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
  \STATE Initialize variables \\
  \STATE Declare list of PV panels, controllers, batteries, and inverters data and cost \\
%  \STATE Declare list of controllers data and cost \\
%  \STATE Declare list of batteries data and cost \\
%  \STATE Declare list of inverters data and cost \\
  \STATE Declare the maximum possible cost $MaxCost$  \\
  \STATE Declare power demand, power peak, energy consumption \\
  \STATE Declare battery autonomy, deep of discharge, AC voltage \\
  \FOR {$HintCost=0$ to $MaxCost$}
 	\STATE Declare non-deterministic variable to select PV Panel from list \\
 	\STATE Declare non-deterministic variable to select Controller from list \\
 	\STATE Declare non-deterministic variable to select Battery from list \\
 	\STATE Declare non-deterministic variable to select Inverter from list \\ 	
 	\STATE Calculate $E_{corrected}, \, E_{p} $ \\
	\STATE Calculate $N_{TPmin}, \, N_{PSmin}, N_{PPmin} $ \\
 	\STATE Calculate $C_{bank}$ \\
	\STATE Calculate $N_{BS}min, \, N_{BP}min, \, N_{B}total$ \\
	\STATE Requirement enforced by \textbf{assume}$(V_{c})$ \\
 	\STATE Calculate $I_{sc,amb}$ \\
 	\STATE Calculate $I_{c,min}$ \\
 	\STATE Requirement enforced by \textbf{assume}$(I_{c} \wedge V_{in}DC \wedge V_{out}AC)$ \\
%	\STATE Requirement enforced by \textbf{assume}$(V_{in}DC \wedge V_{out}AC )$ \\
%	\STATE Requirement enforced by \textbf{assume}$(V_{out}AC)$ \\
	\STATE Requirement enforced by \textbf{assume}$(Demand \wedge P_{surge})$ \\
%	\STATE Requirement enforced by \textbf{assume}$(P_{surge})$ \\
	\STATE non-deterministic variables hold feasible equipment and cost  \\
	\STATE $F_{obj} \leftarrow  N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost} \, + \, Installation_{Cost} \, + \, batrep_{Cost} \, + \, PWO\&M_{Cost}$ \\
	\STATE Violation check with \textbf{assert}$(F_{obj} > HintCost)$ \\
  \ENDFOR
 \RETURN $(\,)$ 
 \end{algorithmic} 
 \label{alg:verification-algorithm}
 \end{algorithm}
%

@@

%---------------------------------------------------------------------------
\section{Case Studies and Analysis}
\label{sec:Results}
%---------------------------------------------------------------------------

This section presents the case studies used to evaluate our proposed approach. We also compare our approach with a specialized simulation tool (HOME Pro). The computing setup, the objectives of the experimental phase, and the results itself are also described.

@@

We have performed seven case studies to evaluate our proposed synthesis approach, as described in the first column of Table~\ref{tab1} (named Specification). These case studies were defined based on real houses visited by the team of a Newton Fund project in riverside communities around the Low Black River in Amazonas - Brazil. For all cases, a estimated load curve (kWh) was defined based on the electronics consumers found of each house.

@@

@@

The start-of-art verification tool, CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} was used as our verification engine to compare our approach effectiveness and efficiency. The Simulation tool HOMER Pro version $3.13.1$ was used for comparative purpose.

@@

\item[EQ2] \textbf{(performance)} how does our formal synthesis tools compares to a specialized simulation tool?

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion and Future Work}
\label{sec:Conclusion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
